---
title: "`Final.Project.10`  Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Final.Project.10}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Source: <https://github.com/AU-R-Data-Science/Final.Project.10>

GitHub repository: `Final.Project.10`

Package: `Final.Project.10`

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>"
)
```


## Introduction

The `Final.Project.10` package in based on the final project assignment of STAT-6210

```{r setup}
library(Final.Project.10)
```


The available functions allow the user to input data sets to fit a logistic regression. The output includes: 1. estimated logistic regression model parameters; 2. initial values of the parameters; 3. confidence intervals for each parameter; 4. fitted logistic regression curves; 5. confusion matrix; 6. six metrics based on default cut-off values (Prevalence, Accuracy, Sensitivity, Specificity, False Discovery Rate and Diagnostic Odds Ratio) and 7. metrics with different cut-off values.

This document shows the usage and output of the functions in `Final.Project.10`, using the `Weekly` dataset from the `ISLR` package and the `mtcars` dataset as examples. The `Weekly` dataset described the weekly percentage returns for the S&P 500 stock index between 1990 and 2010. And the `mtcars` was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973--74 models).

## Data Pre-Processing

As an example, here we utilize the dataset `Weekly` from package `ISLR`
```{r}
library(ISLR)
str(Weekly)
```

The `Weekly` dataset has 1089 observations which contains 9 attributes, where `Lag1`, `Lag2`, `Lag3`, `Lag4`, `Lag5` and `Volume`, can be used as predictor, and `Direction` can be used as response. The `mtcars` has 32 observations which contains 11 attributes, where `mpg`, `dis` and `hp` can be used as predictor, and `vs` can be used as response.

It is important to note that the response values referenced in the functions available in this package need to be in factor format. Therefore, the `vs` variable in `mtcars` should be converted to factor format before calling the function.


We want to take only the parameters `Lag1`, `Lag2`, `Lag3`, `Lag4`, `Lag5` and `Volume` as input.
```{r}
Training.set.1 <- Weekly
head(Training.set.1)
```


```{r}
X_train <- Training.set.1[,2:7]
y_train <- Training.set.1[,9]
```


## Train the model
Use the function `logistic.regression()` to fit the model. Note that the parameter `Y` must be factors.
```{r}
fit <- logistic.regression(X_train, y_train, # required
                           cutoff = 0.5,     # If you don't specify, the default will be 0.5
                           alpha = 0.1,      # If you don't specify, the default will be 0.1
                           B = 20)            # If you don't specify, the default will be 20
```

The user is able to choose the significance level \alpha to obtain for the 1−\alpha confidence intervals for \beta, as well as the cutoff value,  where the default value is set to *0.1* and *0.5*, respectively.

The user is also able to choose the number of bootstraps which by default will be *20*.


## Chech the optimization parameters
Initial values for optimization obtained from the least-squares:
```{r}
optimization <- fit$Beta
knitr::kable(optimization)
```

The optimal \Beta is the same when we use the embeded `glm` method of R:
```{r}
fit.glm <- glm(data = Weekly, Direction~Lag1+Lag2+Lag3+Lag4+Lag5+Volume, family = binomial)
fit.glm$coefficients
```



## Predict and Inspect the output
The bootstrap process was performed when we called `logistic.regression` function.
From that we obtain the resulting confusion matrix using a cut-off value for prediction at 0.5:
```{r}
confusion_Matrix <- fit$Confusion.Matrix
knitr::kable(confusion_Matrix)
```


And all the statistical metrics, including `Prevalence`, `Accuracy`, `Sensitivity`, `Specificity`, `False Discovery Rate`, and `Diagnostic Odds Ratio`, can be output by:
```{r}
fit$Metrics
```


Too see how the metrics vary when we use different cut-off values, check the `Metrics Table`:
```{r}
metrics.table <- fit$'Metrics Table'
knitr::kable(metrics.table)
```

We can see that some of the value in this table became NaN or Inf, that is because when the cut-off value is too small or too high, the model may classify all the test data to be positive or all negative, which will make the denominator to be 0 in the calculation.


## Visualization of output:
The possibility for the user to plot of any of the above metrics evaluated over a grid of cut-off values for prediction going from 0.1 to 0.9 with steps of 0.1.



```{r}
library(ISLR)
Training.set.1 <- Weekly
Training.set.2 <- mtcars
head(Training.set.1)
head(Training.set.2)
Training.set.2$vs <- as.factor(Training.set.2$vs)
```

## Fitted Logistic curve

To demonstrate the function `logistic_plot()` for plotting logistic curves in packages, this section uses `mtcars` as the dataset, where `mpg`, `dis` and `hp` are used as predictors and `vs` is used as the response. The output of the `logistic_plot()` function is in list format, which contains the logistic regression curves for each predictor. For example, in this example the first element represents the logistic regression curve between `mpg` and `vs`, the second element represents the logistic regression curve between `disp` and `vs`, and the third element represents the logistic regression curve between `hp` and `vs`.

```{r}
logistic_plot(X=Training.set.2[,c("mpg","disp","hp")],Y=Training.set.2[,"vs"])
```
